Glasgow Hackerspace CIC Articles of Association

### 2024-03-02 articles.tex
Fix strange TOC formatting originating in titlesec 'runin' argument

\documentclass[12pt]{article}
%\usepackage[scaled]{helvet}
%\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[a4paper, margin=0.5in]{geometry}
% \usepackage{graphicx} % Required for inserting images
\usepackage{hang}
% \usepackage{endnotes}
\usepackage[indentafter]{titlesec}
\usepackage[singlespacing]{setspace}
\usepackage{changepage}
\usepackage{ragged2e}
% Colourisation of certain clauses
%'
%' As regards to colour (like red text in the template we used),
%' use the \textcolor command directly on the block of text which is to
%' be coloured, not, e.g. wrapping a whole \itemize list or wrapping a
%' \subsection{} list.
%'
%' The reason for this is that the section numbering looks odd,
%' and for some reason it also introduces a spurrious new-line before the
%' list or section. It also seems to affect the indentation, even though
%' the only thing which changes is the colour.
\usepackage{xcolor}

@@

% Custom section formatting
%'
%' This compliments the section numbering above: note no argument
%' \thesection in \section*'s \titleformat incantation.
%'
%' The hang part in sub-/sub-sub-sections is pretty important.
%' The text otherwise appears at the very start of the next line!
%' I don't know why block doesn't work like this.
%' I just tried each titlesec shape option in the manual until I found
%' this one worked best.
%'
%' The desired behaviour of indentation of subsequent text is actually in
%' conflict with the expected behaviour. The expected behaviour is that
%' subsequent text should be aligned with the section body, which it is,
%' as our sub-/sub-sub-sections are not indented.
%'
%' Actually getting it to be aligned with the section body was fairly
%' difficult. One trick which works is to have the section body be a
%' text-box with a predictable indentation from the line, and also to
%' align the box to the left.
%'
%' I have defined a variable \clauseident which is inherited by the
%' sub/sub-sub-sections' as well as the \hangindent. I think it looks
%' good if those are roughly the same size.
%'
%' The neat suggestion to use a text box was adapted from the following TeX StackExchange answer: https://tex.stackexchange.com/questions/405372/align-section-with-text-body/405373#405373
%'
\def\clauseindent{30pt}
\def\fakecolour{black}

\titleformat{\section}[runin]% Section to customise
            {\Large\bfseries}% Title text format
            {}%                Title body
            {0pt}%             Horizontal separation between label/title body
            {}%                Space before title body
            []%                Space after title body
\titleformat{\subsection}[hang]{\raggedright\bfseries}{\makebox[\clauseindent][l]{\thesubsection.}}{0pt}{}
\titleformat{\subsubsection}[hang]{\raggedright\mdseries}{\makebox[\clauseindent][l]{\thesubsubsection.}}{0pt}{}

@@

\newpage\section*{Directors}
\addcontentsline{toc}{section}{Directors}
\vspace{1.5\baselineskip}\section*{Directors' Powers and Responsibilities}
\addcontentsline{toc}{section}{Directors' Powers and Responsibility}

@@

\newpage\section*{Members}
\addcontentsline{toc}{section}{Members}
\vspace{1.5\baselineskip}\section*{Becoming and Ceasing to be a Member}
\addcontentsline{toc}{section}{Becoming and Ceasing to be a Member}

>>>>

\documentclass[12pt]{article}
%\usepackage[scaled]{helvet}
%\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[a4paper, margin=0.5in]{geometry}
% \usepackage{graphicx} % Required for inserting images
\usepackage{hang}
% \usepackage{endnotes}
\usepackage[indentafter]{titlesec}
\usepackage{titletoc}
\usepackage{etoolbox}
\usepackage[singlespacing]{setspace}
\usepackage{changepage}
\usepackage{ragged2e}

% Colourisation of certain clauses
%'
%' As regards to colour (like red text in the template we used),
%' use the \textcolor command directly on the block of text which is to
%' be coloured, not, e.g. wrapping a whole \itemize list or wrapping a
%' \subsection{} list.
%'
%' The reason for this is that the section numbering looks odd,
%' and for some reason it also introduces a spurrious new-line before the
%' list or section. It also seems to affect the indentation, even though
%' the only thing which changes is the colour.
\usepackage{xcolor}

@@

% Custom section formatting
%'
%' This compliments the section numbering above: note no argument
%' \thesection in \section*'s \titleformat incantation.
%'
%' The 'hang' part in sub-/sub-sub-sections is pretty important.
%' The text otherwise appears at the very start of the next line!
%' I don't know why block doesn't work like this.
%' I just tried each titlesec shape option in the manual until I found
%' this one worked best.
%'
%' Equally, setting 'runin' instead of 'hang' for section caused weird
%' indentation issues in the TOC, but because the titles are short,
%' had no apparent advantage.
%'
%' The desired behaviour of indentation of subsequent text is actually in
%' conflict with the expected behaviour. The expected behaviour is that
%' subsequent text should be aligned with the section body, which it is,
%' as our sub-/sub-sub-sections are not indented.
%'
%' Actually getting it to be aligned with the section body was fairly
%' difficult. One trick which works is to have the section body be a
%' text-box with a predictable indentation from the line, and also to
%' align the box to the left.
%'
%' I have defined a variable \clauseident which is inherited by the
%' sub/sub-sub-sections' as well as the \hangindent. I think it looks
%' good if those are roughly the same size.
%'
%' The neat suggestion to use a text box was adapted from the following TeX StackExchange answer: https://tex.stackexchange.com/questions/405372/align-section-with-text-body/405373#405373
%'
\def\clauseindent{30pt}
\def\fakecolour{black}

% \titleformat{\section}[hang]{\centering\bfseries\Large}{\thesection}{0pt}{}[]
\titleformat{\section}[hang]{\bfseries\Large}{\thesection}{0pt}{}[]
\titleformat{\subsection}[hang]{\raggedright\bfseries}{\makebox[\clauseindent][l]{\thesubsection.}}{0pt}{}
\titleformat{\subsubsection}[hang]{\raggedright\mdseries}{\makebox[\clauseindent][l]{\thesubsubsection.}}{0pt}{}

% Fix weird indentation of TOC start
% https://tex.stackexchange.com/questions/269711/titlesec-toc-formatting-capitalization-subsection-numbering-for-sections-ti

@@

\newpage\section*{\huge{Directors}}
\addcontentsline{toc}{section}{Directors}
\section*{Directors' Powers and Responsibilities}
\addcontentsline{toc}{section}{Directors' Powers and Responsibility}

@@

\newpage\section*{\huge{Members}}
\addcontentsline{toc}{section}{Members}
\section*{Becoming and Ceasing to be a Member}
\addcontentsline{toc}{section}{Becoming and Ceasing to be a Member}
